\myfont Implementation and evaluation of register allocation for translating LLVM-{}- to x86-64

### 2024-01-11 article.tex
Update intervalenvds

\begin{figure}[H]
  \centering
   \begin{minipage}[b]{0.95\textwidth}
     \centering
     \begin{minted}[linenos,bgcolor=LightGray]{ocaml}
let intervalends insns starts (in_, out) =
  let insn (i, _n) (ordstarts, lengths, ends, active) =
    let in' = S.SS.diff (S.SS.union in_.(i) out.(i)) active in
    ( S.SS.fold (fun e a -> IT.update i (add e) a) in' ordstarts,
      S.SS.fold
        (fun e a -> IT.update (-i + S.ST.find e starts) (add e) a)
        in' lengths,
      S.SS.fold (fun e a -> S.ST.add e i a) in' ends,
      S.SS.union active in' )
  in
  List.fold_right insn insns (IT.empty, IT.empty, S.ST.empty, S.SS.empty)
     \end{minted}
     \caption{Implementation of \texttt{intervalendsintervalstart} in \texttt{lib/linear.ml}}\label{fig:intervalends.ml}
   \end{minipage}
\end{figure}

\noindent The opposite is quite similar (see Figure \ref{fig:intervalends.ml}).

>>>>

\begin{figure}[H]
  \centering
   \begin{minipage}[b]{0.95\textwidth}
     \centering
     \begin{minted}[linenos,bgcolor=LightGray]{ocaml}
let intervalends insns (in_, out) =
  let insn (i, _n) (ordends, ends, active) =
    let in' = S.SS.diff (S.SS.union in_.(i) out.(i)) active in
    ( S.SS.fold (fun e a -> IT.update i (add e) a) in' ordends,
      S.SS.fold (fun e a -> S.ST.add e i a) in' ends,
      S.SS.union active in' )
  in
  List.fold_right insn insns (IT.empty, S.ST.empty, S.SS.empty)
     \end{minted}
     \caption{Implementation of \texttt{intervalendsintervalstart} in \texttt{lib/linear.ml}}\label{fig:intervalends.ml}
   \end{minipage}
\end{figure}

\noindent The opposite is quite similar (see Figure \ref{fig:intervalends.ml}), with the only real difference being the use of \texttt{List.fold\_right} instead of \texttt{List.fold\_left} to reduce the function body in reverse.
